International Transport costs:...

### 2020-06-15 redaction/DP_CEPII/dhp_mise_en_forme_cepii.tex

\documentclass[a4paper,11pt]{article}

%\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
%\usepackage[latin1]{inputenc}
%\usepackage{hyperref}
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
%%GD Quand je mets usepackage[utf8]{inputenc} je n'arrive plus à compiler la biblio
%J'ai essayé de débuger : je n'y suis pas arrivé
\usepackage{rotating}
\usepackage{setspace}
\usepackage{lscape}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{vmargin}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage[tableposition=top]{caption}
\usepackage{amsfonts}
\usepackage{bbold}
\usepackage{bbm}
\usepackage[flushleft]{threeparttable}
%\usepackage{bbold}
%\usepackage[T1]{fontenc}
% JH : impossible de compiler avec le package bbold, remplacé par amsfonts
% LP : impossible de compiler avec le package bbold, remplacé par bbm
\usepackage{upgreek}
\usepackage{comment}
\includecomment{commentGD}
\usepackage[draft]{todonotes}
%\usepackage[disable]{todonotes}
%%GDPour cacher les notes, \usepackage[disable]{todonotes}

@@

@@

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We are grateful to Olger G\"{o}rg, S\'{e}bastien Jean, Vincent Vicard for their insightful comments. The paper has greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the Universites of California-Irvine, Paris-Dauphine, Paris-I, Nancy and the the Kiel Institute for the World Economy.
Finally, any remaining errors are ours.
This paper was partly funded by an University grant from Lille-I University.
It features an online appendix containing additional results and available on the authors' websites.}}

\author{Guillaume \textsc{Daudin}\thanks{%
Universit\'{e} Paris-Dauphine \& PSL University, IRD, LEDa, UMR 225, DIAL, 75016 PARIS, FRANCE \newline
Sciences Po, Observatoire Fran\c{c}ais des Conjonctures \'{E}conomiques (OFCE), 75014 PARIS, FRANCE \newline
; email: \url{guillaume.daudin@dauphine.fr}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France; email: \url{jerome.hericourt@univ-lille.fr}}\qquad Lise \textsc{Patureau}\thanks{Corresponding author.
Universit\'{e} Paris-Dauphine \& PSL University, LEDa, 75016 PARIS, FRANCE;  email: \url{lise.patureau@dauphine.fr} } }

\date{June 2018}
 \maketitle
\bigskip

\begin{abstract}
This paper investigates the pattern of international transport costs over time, using information contained in the US imports flows over 1974-2013. First, we document the importance of the per-unit (additive) component of transport costs. We thus find that additive costs are quantitatively sizable, representing between one third and one half of overall transport costs. Second, we identify the respective roles of the reduction in ``pure'' transport costs and trade composition effects in the downward trend of international transport costs, in the same spirit as \cite{hummels2007}. Unlike him, we find that trade composition effects do not matter much and, when they do, they tend to amplify (rather than reduce) the decrease in pure transport costs. Importantly, this difference of results can be attributed to the new way of modeling the per-unit component of transport costs we offer. In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
\end{abstract}

\thispagestyle{empty} \pagestyle{plain} \setcounter{page}{1}

\bigskip

\noindent \emph{JEL classification}: F14, N70, R40 \\
\noindent \emph{Keywords}: Transport costs estimates, non-linear econometrics, period 1974-2013, additive costs, trade composition effects

@@

\begin{figure}[htbp]
\caption{Share of additive costs (3-digit classification)}
\label{fig:part_cout_additif}
\begin{center}
\includegraphics[width=8cm, height=5cm]{part_cout_additif.pdf}
%{\footnotesize {OECD data} }
\end{center}
\end{figure}

@@

As an ultimate check, we investigate whether the varying pattern over time/country of origin/product pointed out in Section \ref{sec:results_decomposition} is also robust to the separability assumption.
To this aim, we replicate Figure \ref{fig:histogram_beta} on the reduced sample for both specifications of separable (baseline) and non-separable fixed costs.
Figure \ref{fig:histogram_beta_robustness} reports the histogram of the distribution of the elasticity of transport costs to the export price ($\beta_{ikt}$, for Air transport (top panel) and for maritime transport (bottom panel) under the baseline specification (Panels (a, (c))) and the non-separability scenario (Panels (b), (c)).

@@

\newpage
\bibliographystyle{essaien}
\bibliography{biblio}

@@

\clearpage

%\appendix
\setcounter{table}{0}
\renewcommand{\thefigure}{A.\arabic{figure}}
\renewcommand{\thetable}{A.\arabic{table}}

\section{Data Appendix \label{app:data}}

@@

\section{Estimation at the 3-digit classification level \label{app:more_results}}

\subsection{Transport costs estimates: More detailed results}

@@

\subsection{Assessing the importance of additive transport costs \label{app:diagnostic_test}}

@@

\subsection{Variance decomposition exercise \label{app:decomp_variance}}

@@

\section{Estimation at the 4-digit level \label{app:4digit}}

@@

\subsection{Transport cost estimates}

@@

\subsection{Goodness-of-fit tests at the 4-digit level}

@@

\section{Eliminating the composition effects: More details \label{app:comp-effects}}

@@

\subsection{More on our methodology}

@@

\subsection{Comparing with \cite{hummels2007} \label{app:compare_Hummels}}

>>>>

%\documentclass[a4paper,11pt]{article}
\documentclass{cepiiwp2014}
%\usepackage[pdftex]{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage[frenchb,english]{babel}
\usepackage{graphics}
\usepackage{graphicx}
%\pagestyle{headings}
\usepackage{amsmath}
\usepackage{array}
\usepackage{booktabs}
\everymath{\displaystyle}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[authoryear]{natbib}
\usepackage{hyperref}
\usepackage{pict2e}
\parindent=0cm
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\definecolor{perso}{cmyk}{1,0,0,0}
%\hypersetup{linkcolor=perso}YellowGreen
\usepackage[usenames,dvipsnames]{color}
\hypersetup{colorlinks=true,linkcolor=blue, citecolor=Blue, urlcolor=Blue}
\usepackage{setspace}
%\onehalfspacing
\doublespacing
\usepackage{lscape}
\setlength{\bibhang}{1.5em}
\usepackage{relsize,exscale}
\usepackage{pstricks}
\setlength{\unitlength}{1cm}
\usepackage{threeparttable}
\usepackage{floatrow}
\usepackage[tableposition=top]{caption}
\floatsetup[table]{capposition=top}
\floatsetup[figure]{capposition=top}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath}
%\usepackage[latin1]{inputenc}
%\usepackage{hyperref}
%\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
%%GD Quand je mets usepackage[utf8]{inputenc} je n'arrive plus à compiler la biblio
%J'ai essayé de débuger : je n'y suis pas arrivé
\usepackage{rotating}
\usepackage{setspace}
\usepackage{lscape}
%\usepackage[round]{natbib}
\usepackage[authoryear]{natbib}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{vmargin}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage[tableposition=top]{caption}
\usepackage{amsfonts}
\usepackage{bbold}
\usepackage{bbm}
%\usepackage[flushleft]{threeparttable}
%\usepackage{bbold}
%\usepackage[T1]{fontenc}
% JH : impossible de compiler avec le package bbold, remplacé par amsfonts
% LP : impossible de compiler avec le package bbold, remplacé par bbm
\usepackage{upgreek}
%\usepackage{comment}
%\includecomment{commentGD}
%\usepackage[draft]{todonotes}
%\usepackage[disable]{todonotes}
%%GDPour cacher les notes, \usepackage[disable]{todonotes}

@@

\title{International Transport costs:...}

@@

\maketitle

\begin{affiliation}[International Transport costs:\\New Findings from modeling additive costs\footnote{We are grateful to S\'{e}bastien Jean, Vincent Vicard, and participants at ETSG 17\textsuperscript{th} meetings in Helsinki, DEGIT XXII in Paris School of Economics, and participants at seminars of the University of California-Irvine, the Universities of Paris-Dauphine, Paris-I and Nancy for very useful discussions.
Finally, any remaining errors are ours.
This paper features an online appendix containing additional results and available on the authors' websites.}]

\urlstyle{rm}

Guillaume Daudin\footnote{Universit\'{e} Paris-Dauphine \& PSL University, IRD, LEDa, UMR 225, DIAL; Sciences Po, Observatoire Fran\c{c}ais des Conjonctures \'{E}conomiques (OFCE); Email: \url{guillaume.daudin@dauphine.fr}} and J\'{e}r\^{o}me Hericourt\footnote{Universit\'{e} de Lille, LEM, UMR CNRS 9221, and CEPII; Email: \url{jerome.hericourt@univ-lille.fr}} and Lise Patureau\footnote{Corresponding author. Universit\'{e} Paris-Dauphine \& PSL University, LEDa; Email: \url{lise.patureau@dauphine.fr}}

\end{affiliation}

 \maketitle
\bigskip

%\begin{abstract}
%This paper investigates the pattern of international transport costs over time, using information contained in the US imports flows over 1974-2013. First, we document the importance of the per-unit (additive) component of transport costs. We thus find that additive costs are quantitatively sizable, representing between one third and one half of overall transport costs. Second, we identify the respective roles of the reduction in ``pure'' transport costs and trade composition effects in the downward trend of international transport costs, in the same spirit as \cite{hummels2007}. Unlike him, we find that trade composition effects do not matter much and, when they do, they tend to amplify (rather than reduce) the decrease in pure transport costs. Importantly, this difference of results can be attributed to the new way of modeling the per-unit component of transport costs we offer. In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
%\end{abstract}

%\thispagestyle{empty} \pagestyle{plain} \setcounter{page}{1}

%\noindent \emph{JEL classification}: F14, N70, R40 \\
%\noindent \emph{Keywords}: Transport costs estimates, non-linear econometrics, period 1974-2013, additive costs, trade composition effects

@@

\begin{figure}[htbp]
\caption{Share of additive costs (3-digit classification)}
\label{fig:part_cout_additif}
\begin{center}
\includegraphics[width=10cm, height=7cm]{part_cout_additif.pdf}
%{\footnotesize {OECD data} }
\end{center}
\end{figure}

@@

As an ultimate check, we investigate whether the varying pattern over time/country of origin/product pointed out in Section \ref{sec:results_decomposition} is also robust to the separability assumption.
To this aim, we replicate Figure \ref{fig:histogram_beta} on the reduced sample for both specifications of separable (baseline) and non-separable fixed costs.
Figure \ref{fig:histogram_beta_robustness} reports the histogram of the distribution of the elasticity of transport costs to the export price ($\beta_{ikt}$), for Air transport (top panel) and for maritime transport (bottom panel) under the baseline specification (Panels (a), (c)) and the non-separability scenario (Panels (b), (c)).

@@

\newpage
\bibliographystyle{elsarticle-harv}

%\section*{References}
\bibliography{biblio}

@@

%\clearpage

\setcounter{table}{0}
\renewcommand{\thefigure}{A.\arabic{figure}}
\renewcommand{\thetable}{A.\arabic{table}}

\subsection{Data Appendix \label{app:data}}

@@

\subsection{Estimation at the 3-digit classification level \label{app:more_results}}

\subsubsection{Transport costs estimates: More detailed results}

@@

\subsubsection{Assessing the importance of additive transport costs \label{app:diagnostic_test}}

@@

\subsubsection{Variance decomposition exercise \label{app:decomp_variance}}

@@

\subsection{Estimation at the 4-digit level \label{app:4digit}}

@@

\subsubsection{Transport cost estimates}

@@

\subsubsection{Goodness-of-fit tests at the 4-digit level}

@@

\subsection{Eliminating the composition effects: More details \label{app:comp-effects}}

@@

%\subsubsection{More on our methodology}

@@

\subsubsection{Comparing with \cite{hummels2007} \label{app:compare_Hummels}}
